---
title: "Diamond sizes"
date: 2016-08-25
output: html_document
---

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)

smaller <- diamonds |> 
  filter(carat <= 2.5)
```

We have data about `r nrow(diamonds)` diamonds. Only 
`r nrow(diamonds) - nrow(smaller)` are larger than
2.5 carats. The distribution of the remainder is shown
below:

```{r, echo = FALSE}
smaller |> 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```
#PROBLEM 1
```{r, include = TRUE}
#QUESTION 2
smallerToLarger <- diamonds |>
  arrange(x,y,z)

```
The diamonds data set is arranged from smaller to larger using the variables x, y, and z.

```{r, include = TRUE}
largest <- slice_tail(smallerToLarger, n=20)
knitr::kable(largest)
```
The tail of the arranged dataset is trimmed, getting the last 20 (which are the largest dimonds). Then the formatted table is produced.

```{r}
#QUESTION 3
larger <- diamonds |>
  filter(carat >= 2.5)

#percent larger than or equal to 2.5 carat
percentDiamonds <- ((nrow(larger)/nrow(diamonds))*100)

#Using comma() function to produce nice format
comma <- function(x) format(x, digits = 2, big.mark = ",")

cat("The percentage of diamonds larger than or equal to 2.5 carat is", comma(percentDiamonds), "%")
```
#PROBLEM 2
```{r}
#QUESTION 1


```



#PROBLEM 3

#QUESTION 1


#QUESTION 2
aproxfun() given two or more vectors, this function returns a list of points that are between the given vectors. If these points are plotted we can see that the list will connect the vectors as points in the plane.

ecdf() it stands for Empirical Cumulative Distribution Function. The input is a vector, it calculates the cumulative probability for each as the number of observations less than or equal to a given observation divided by the total number of observations in the vector. The output is a list with these values.


```{r}
#QUESTION 5
i <- 0
new_counter2 <- function() {
  i <<- i + 1
  i
}

```


```{r}
#QUESTION 6
new_counter3 <- function() {
  i <- 0
  function() {
    i <- i + 1
    i
  }
}
```

